AggregateCounts

### 2021-06-07 R/AggregateCounts.Rmd
plotting aggregate vs planktonics for wtd1_02

#create histograms, this takes a long time, so consider cutting them in chunks
allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
allDataList<- group_split(allDataGrouped)#create list of dataframes
allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list

allDataHistograms.5df<- bind_rows(allDataHistograms.5)

```
```{r Histogram fucntions}
FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
  results<-data.frame()
  for( i in 1:(length(sec)-1)){ 
    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
    if(blah$frequency>0){ 
      results<-rbind(results, blah)} 
  }
  return(results) 
}
TotalFancyHistogram<-function(df,binsize){
  totalbiomass<-sum(df$Size)#total biomass per sample
  totalfrequency<-length(df$Size)#total number of objects
  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomas per bin
  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
  histogram%>%mutate(Condition=df$Condition[1])->histogram
  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
  histogram%>%mutate(Sample=df$Sample[1])->histogram
  return(histogram)
}
```

>>>>

#Create histograms
##this takes a long time, so consider running them in parts
allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
#allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition, Sample)# this is to include sample on the distribution or keep it out
allDataList<- group_split(allDataGrouped)#create list of dataframes
allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
allDataHistograms.5df<- bind_rows(allDataHistograms.5)#bring them together

#Separating aggregates vs planktonic
hist.plank.Agg.Sumary<-allDataHistograms.5df %>%  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",max>5 ~ "Aggregate")) %>%
  ungroup() %>%group_by(Species, TimePoint, Condition,Aggregation) %>% 
  summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))

hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation),
            SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation))

#Plotting these guys
PlotAggsPlank<- function(){
  ggplot()+
    geom_col(data = hist.plank.Agg.Stats,aes(x=TimePoint,y=MeanBiomass, fill = Aggregation),size=3,position = position_dodge( width = .9))+
    geom_errorbar(data = hist.plank.Agg.Stats,aes(x=TimePoint,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass),size=.5,position = position_dodge2( width = .6))+
    facet_grid(.~Species)+
    labs(title = "Chronic Wounds", x = "", y = "Biomass contribution")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotAggsPlank()

```
```{r Histogram functions}
FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
  results<-data.frame()
  for( i in 1:(length(sec)-1)){ 
    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
    if(blah$frequency>0){ 
      results<-rbind(results, blah)} 
  }
  return(results) 
}
TotalFancyHistogram<-function(df,binsize){
  totalbiomass<-sum(df$Size)#total biomass per sample
  totalfrequency<-length(df$Size)#total number of objects
  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomas per bin
  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
  histogram%>%mutate(Condition=df$Condition[1])->histogram
  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
  histogram%>%mutate(Sample=df$Sample[1])->histogram
  return(histogram)
}
```
